Appendix

### 2025-04-09 manuscript_rmarkdown/manuscript_appendix.Rmd
Harmonise styling.

# Appendix A: Log-likelihood functions for location and scale invariant power transformation

Location and scale-invariant Box-Cox and Yeo-Johnson transformations are parametrised using location $x_0$ and scale $s$ parameters, in addition to transformation parameter $\lambda$.
This leads to the following transformations. The location and scale-invariant Box-Cox transformation is:

```{=latex}
\begin{equation}
\phi_{\text{BC}}^{\lambda, x_0, s} (x_i) = 
\begin{cases}
\left( \left(\frac{x_i - x_0}{s} \right)^\lambda - 1 \right) / \lambda & \text{if } \lambda \neq 0\\
\log\left[\frac{x_i - x_0}{s}\right] & \text{if } \lambda = 0
\end{cases}
\end{equation}
```
where $x_i - x_0 > 0$.
The location and scale-invariant Yeo-Johnson transformation is:

@@

Results for Box-Cox transformations are shown in Table
\ref{tab:clean-transformation-appendix-residuals-bc},
\ref{tab:clean-transformation-appendix-lambda-bc},
and \ref{tab:clean-transformation-appendix-p-value-bc}.
Additionally, results for Yeo-Johnson transformations are shown in Table
\ref{tab:clean-transformation-appendix-residuals-yj},
\ref{tab:clean-transformation-appendix-lambda-yj},
and \ref{tab:clean-transformation-appendix-p-value-yj}.
As may be observed, in these examples robust location and shift-invariant 
transformations have higher residual errors because of low weights being
assigned to tails of a distribution. This is also shown in 
Tables \ref{tab:comparison_methods_simulations_yeo_johnson}
and \ref{tab:comparison_methods_simulations_box_cox} for clean data without outliers.

>>>>

# Appendix A: Log-likelihood functions for location- and scale-invariant power transformation

Location- and scale-invariant Box-Cox and Yeo-Johnson transformations are parametrised using location $x_0$ and scale $s$ parameters, in addition to transformation parameter $\lambda$.
This leads to the following transformations. The location- and scale-invariant Box-Cox transformation is:

```{=latex}
\begin{equation}
\phi_{\text{BC}}^{\lambda, x_0, s} (x_i) = 
\begin{cases}
\left( \left(\frac{x_i - x_0}{s} \right)^\lambda - 1 \right) / \lambda & \text{if } \lambda \neq 0\\
\log\left[\frac{x_i - x_0}{s}\right] & \text{if } \lambda = 0
\end{cases}
\end{equation}
```
where $x_i - x_0 > 0$.
The location- and scale-invariant Yeo-Johnson transformation is:

@@

Results for Box-Cox transformations are shown in Table
\ref{tab:clean-transformation-appendix-residuals-bc},
\ref{tab:clean-transformation-appendix-lambda-bc},
and \ref{tab:clean-transformation-appendix-p-value-bc}.
Additionally, results for Yeo-Johnson transformations are shown in Table
\ref{tab:clean-transformation-appendix-residuals-yj},
\ref{tab:clean-transformation-appendix-lambda-yj},
and \ref{tab:clean-transformation-appendix-p-value-yj}.
As may be observed, in these examples robust location- and shift-invariant 
transformations have higher residual errors because of low weights being
assigned to tails of a distribution. This is also shown in 
Tables \ref{tab:comparison_methods_simulations_yeo_johnson}
and \ref{tab:comparison_methods_simulations_box_cox} for clean data without outliers.
